%-------------------------
% Resume in Latex
% Author: Adapted for Tejas
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
% \input{glyphtounicode}  % pdfTeX-only; tectonic uses XeTeX

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.9in}
\addtolength{\textheight}{1.9in}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \scshape\raggedright\normalsize\bfseries
}{}{0em}{}[\color{black}\titlerule]
\titlespacing{\section}{0pt}{3pt plus 1pt minus 1pt}{2pt}

% \pdfgentounicode=1  % pdfTeX-only

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Tejas} \\ \vspace{2pt}
    \small \faPhone\ 9817135031 ~
    \href{mailto:tejas06012005@gmail.com}{\faEnvelope\ \underline{tejas06012005@gmail.com}} ~
    \href{https://www.linkedin.com/in/tejas-kashyap-1450a2252/}{\faLinkedin\ \underline{linkedin.com/in/tejas-kashyap-1450a2252/}}
\end{center}


%-----------SKILLS-----------
\section{Skills}
\textbf{Languages:} Python, C++, AppScript \\
\textbf{GenAI \& LLM:} Groq, Google Gemini, LangChain, LangGraph, RAG, Multi-Agent Systems, Hallucination Mitigation \\
\textbf{Vector DBs:} ChromaDB, Pinecone, FAISS, LaBSE embeddings (cross-lingual) \\
\textbf{ML/DL:} TensorFlow, Keras, PyTorch, Transfer Learning, ONNX (edge inference), Federated Learning (Flower), YOLOv5 \\
\textbf{Deployment:} FastAPI, Docker, Raspberry Pi 5 home server, Cloudflare Tunnel, Git, Linux \\
\textbf{Practices:} Spec-Driven Development (Claude Code), Idempotent Data Pipelines

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{AI Engineer Intern}{Feb 2026 -- Present}
{Blu Parrot Ventures Pvt. Ltd., Gurgaon}{}

\resumeItemListStart
\resumeItem{Built a \textbf{Document-Grounded QA (DGQA)} system evaluating \textbf{450+ page defense tenders} --- \textbf{Gemini} structured extraction into \textbf{Pydantic} schemas, deterministic \textbf{7-rule eligibility checks}, and weighted bid scoring.}
\resumeItem{Built a production \textbf{farm-advisory API} running \textbf{6 advisory engines} on \textbf{Sentinel-2 NDVI/NDWI} time-series, \textbf{Open-Meteo} weather, and \textbf{Supabase} farm data --- incl. a \textbf{least-cost LP fertilizer optimizer} and \textbf{EVI-regression yield prediction}.}
\resumeItem{Designed a \textbf{versioned agronomy RAG pipeline} with confidence-gated LLM classification, \textbf{evidence-checked ``no-inference'' extraction}, and \textbf{ChromaDB} --- agronomists update knowledge without code deploys.}
\resumeItem{Built a \textbf{LangGraph} multi-source assistant: \textbf{cross-lingual LaBSE retrieval}, a custom \textbf{Wikipedia MCP server}, LLM source-routing; cut request latency \textbf{23s $\rightarrow$ 5--8s} via lifespan model loading.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%-----------RESEARCH-----------
\section{Research}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Temple Waste Detection using YOLOv5} $|$ PyTorch, Roboflow, Python}{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=5739822}{\underline{ICSRF 2025 --- SSRN}}}
\resumeItemListStart
    \resumeItem{Built a \textbf{first-of-its-kind temple waste classification system}, addressing an environmental problem with \textbf{0 prior published research} in this domain.}
    \resumeItem{Collected and manually annotated \textbf{186 original images} across 3 classes, expanded to \textbf{448 labeled samples} via augmentation.}
    \resumeItem{Trained YOLOv5s achieving \textbf{25\% mAP}, \textbf{51\% precision}, \textbf{23\% recall}, and \textbf{30 FPS} real-time inference.}
    \resumeItem{Paper accepted and presented at ICSRF 2025; published on SSRN and indexed in Google Scholar.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Smart Agriculture System (Plant Disease Detection)} $|$ TensorFlow, Keras, ONNX, FastAPI, Docker, Raspberry Pi 5}
{\href{https://pifive.marutsut.me/docs\#/default/predict_predict__model_name__post}{\underline{Live API}}}

\resumeItemListStart
    \resumeItem{Benchmarked \textbf{8 CNN families} (VGG-16 $\rightarrow$ MobileNetV3) under one training pipeline on \textbf{PlantVillage (20,638 images, 15 classes)}, comparing accuracy against \textbf{parameters, memory, and on-device latency}.}
    \resumeItem{Identified the edge-efficiency frontier: \textbf{MobileNetV3-Small at 99.95\% accuracy} with \textbf{1.53M parameters} and \textbf{8 ms/image} on a Raspberry Pi 5; EfficientNetB0 matched accuracy at the lowest loss.}
    \resumeItem{Exported all models to \textbf{ONNX} and deployed \textbf{10 of them behind one FastAPI endpoint} on a \textbf{Raspberry Pi 5} (Docker multi-arch, Cloudflare Tunnel) --- live and publicly accessible.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Ekantik Vartalap --- Source-Grounded RAG System} $|$ Python, LangChain, ChromaDB, Groq, FastAPI}{\href{https://ekantik.marutsut.me}{\underline{ekantik.marutsut.me}}}
\resumeItemListStart
    \resumeItem{Built a \textbf{source-grounded Hindi QA system} over 1,300+ discourse videos that responds \textbf{only when an explicit answer exists} and refuses otherwise --- \textbf{zero LLM cost on unanswerable queries}.}
    \resumeItem{Implemented a \textbf{resumable, idempotent ingestion pipeline}: \textbf{1,000+ Hindi transcripts} with \textbf{video-level deduplication} against the vector store.}
    \resumeItem{Indexed \textbf{$\sim$40k transcript chunks} in \textbf{ChromaDB} with \textbf{cross-lingual LaBSE embeddings} --- English queries retrieve Hindi discourse passages directly; answers assembled via a \textbf{constrained generation prompt} with mandatory source citations.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Lens --- Clinical Video Interpreter (Indic Speech AI)} $|$ Sarvam AI, Gemini, FastAPI, Python}{\href{https://lens.marutsut.me}{\underline{lens.marutsut.me}}}
\resumeItemListStart
    \resumeItem{Built an end-to-end pipeline converting \textbf{Hindi/Hinglish doctor--patient consultation videos} into structured assessments: \textbf{Sarvam Saaras v3 batch ASR + speaker diarization} $\rightarrow$ \textbf{Gemini} role assignment and classification.}
    \resumeItem{Implemented \textbf{verbatim-substring hallucination filtering} --- every LLM-classified response is validated against the transcript before acceptance.}
    \resumeItem{Reverse-engineered \textbf{undocumented Sarvam batch-API behaviors} and built a \textbf{diarization-failure fallback} recovering speaker roles from dialogue structure; transcription quality verified with native speakers across Hindi, Hinglish, and Punjabi.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bachelor of Technology in Computer Science Engineering}{2022 -- 2026}
    {Bennett University, Greater Noida}{CGPA: 7.85/10}
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\resumeItemListStart
  \resumeItem{Run a \textbf{Raspberry Pi 5 home server} (\textbf{marutsut.me}) hosting \textbf{3 live public AI services} --- a 10-model plant-disease API, a Hindi RAG system, and a clinical video interpreter --- via Docker and Cloudflare Tunnel.}
  \resumeItem{Built a freestyle Acro drone achieving \textbf{144 km/h top speed} and \textbf{6 km range} with night-vision FPV camera.}
  \resumeItem{Organized a 5-day research event with \textbf{500+ attendees}; received LOR from Dean of Research.}
\resumeItemListEnd

\end{document}
